---
title: "Assignment_9"
author: "Mariana_euan"
date: "`r Sys.Date()`"
output: html_document
---
Here is assignment 9

--- 

title: "Assignment_9" 

author: "Mariana_euan" 

date: "`r Sys.Date()`" 

output: html_document 

--- 

Here is assignment 9 

```{r load_libraries} 

# Load necessary libraries 

library(tidyverse) 

library(caret) 

library(ggplot2) 

library(GGally) 

library(dplyr) 

library(wesanderson) 

  

```{r load_data} 

# Set your working directory 

setwd("C:/Users/Rushe/Desktop/Data_Course_EUAN/Data") 

  

# Load the data 

GradSchool_Admissions <- read.csv("GradSchool_Admissions.csv") 

  

```{r explore_data} 

# Explore the data 

glimpse(GradSchool_Admissions) 

summary(GradSchool_Admissions) 

str(GradSchool_Admissions) 

head(GradSchool_Admissions) 

  

```{r check_na} 

# Check for NA values 

sum(is.na(GradSchool_Admissions)) 

  

```{r create_boxplot} 

# Create the boxplot with custom colors and axis labels 

boxplot(GradSchool_Admissions$gre, main="GRE Scores", boxwex=0.1, col=c("#87CEEB", "#191970"), xlab="Categories", ylab="GRE Scores") 

  

```{r boxplot_gpa} 

# Boxplot of GPA scores by admission status 

boxplot(GradSchool_Admissions$gpa ~ GradSchool_Admissions$admit, main = "Boxplot of GPA Scores by Admission Status", xlab = "Admission Status", ylab = "GPA Score") 

  

  

```{r logistic_regression_model} 

# Logistic regression model 

model <- glm(admit ~ gre + gpa + rank, data = GradSchool_Admissions, family = binomial) 

summary(model) 

  

```{r get_variable_names} 

# Get variable names 

var_names <- names(GradSchool_Admissions) 

print(var_names) 

  

```{r ggpairs_function} 

# Use ggpairs() function 

GradSchool_Admissions %>% 

  select(admit, gre, gpa, rank) %>% 

  ggpairs() 

```{r setup, include=FALSE} 

knitr::opts_chunk$set(echo = TRUE) 

# Load necessary libraries 

library(tidyverse) 

library(caret) 

library(ggplot2) 

library(GGally) 

library(dplyr) 

library(wesanderson) 

# Set your working directory 

setwd("C:/Users/Rushe/Desktop/Data_Course_EUAN/Data") 

  

# Load the data 

GradSchool_Admissions <- read.csv("GradSchool_Admissions.csv") 

``` 

  

```{r GradSchool_Admissions_chunk} 

summary(GradSchool_Admissions) 

# Explore the data 

glimpse(GradSchool_Admissions) 

summary(GradSchool_Admissions) 

str(GradSchool_Admissions) 

head(GradSchool_Admissions) 

  

# Check for NA values 

sum(is.na(GradSchool_Admissions)) 

  

# Create the boxplot with custom colors and axis labels 

boxplot(GradSchool_Admissions$gre, main="GRE Scores", boxwex=0.1, col=c("#87CEEB", "#191970"), xlab="Categories", ylab="GRE Scores") 

  

# Check for incorrect values 

sum(GradSchool_Admissions$gpa < 0 | GradSchool_Admissions$gpa > 4) 

sum(GradSchool_Admissions$gre < 260 | GradSchool_Admissions$gre > 340) 

  

# Check for consistent coding 

table(GradSchool_Admissions$rank) 

  

# Subset data to find GRE scores outside the expected range 

outliers <- GradSchool_Admissions[GradSchool_Admissions$gre < 260 | GradSchool_Admissions$gre > 340, ] 

print(outliers) 

  

# Check the range of GRE scores 

range(GradSchool_Admissions$gre) 

  

# Check for duplicate rows 

duplicates <- GradSchool_Admissions[duplicated(GradSchool_Admissions),] 

print(duplicates) 

  

# Remove duplicate rows 

GradSchool_Admissions <- unique(GradSchool_Admissions) 

  

  

  

  

```{r boxplot} 

# Boxplot of GPA scores by admission status 

boxplot(GradSchool_Admissions$gpa ~ GradSchool_Admissions$admit, main = "Boxplot of GPA Scores by Admission Status", xlab = "Admission Status", ylab = "GPA Score") 

  

```{r logistic_regression} 

# Logistic regression model 

model <- glm(admit ~ gre + gpa + rank, data = GradSchool_Admissions, family = binomial) 

summary(model) 

  

```{r variable_names} 

# Get variable names 

var_names <- names(GradSchool_Admissions) 

print(var_names) 
 

 